Age-related changes in plant growth and traits

### 2015-09-02 RA_figs.rmd
created new file with some large plots, looking at different combinations of variables for each species

@@

>>>>

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "growth_inv"
results$xvar <- "total_weight_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- as.data.frame(results)
results[1:6]

@@

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$yvar <- "growth_inv"
results$xvar <- "leaf_area_0"
results$data <- "SummaryInd"
results$model <- "log10(yvar)~log10(xvar)"
saved_results <- bind_rows(saved_results,results)
results
